---
title: "Political Violence in Nigeria"
subtitle: "Data Analysis Presentation"
author: "Alyssa Glomb"
institute: "American University, SIS 750"
date: "Spring 2023"
output:
  xaringan::moon_reader:
    self_contained: true
    lib_dir: libs
    css: [default, metropolis, rladies-fonts]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
htmltools.dir.version = TRUE, echo=TRUE, fig.width = 14, fig.asp = 0.698, 
        fig.align = 'center', out.width = "85%")

library(tidyverse)
library(knitr)
library(readxl)
library(dplyr)
library(ggplot2)
library(reshape2)
library(magrittr)
library(forcats)

```

# Data Background

- The following information was compiled from the Electoral Contention and Violence (ECAV) dataset. 
- The data was derived from media reports of events and all actions involve violence or protests that are related to elections and politics. 
- The full ECAV dataset was compiled based on events in 136 countries between 1990 and 2012 and includes 39 variables. 
- I am using a subset of the database for this presentation. This analysis is based on the data collected in Nigeria, which has 334 observations of violent events for the variables I analyzed.  

&nbsp;  

<small>
Data Citation:  

Daxecker, Ursula E., Elio Amicarelli and Alexander Jung. 2019. “Electoral Contention and Violence (ECAV): A New Dataset” Journal of Peace Research 56(5): 714-723. https://doi.org/10.1177/0022343318823870

Daxecker, Ursula E., Elio Amicarelli and Alexander Jung. 2019. “Electoral Contention and Violence (ECAV) Codebook.”

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

</small>

---
#Forms of Conflict
##Nigeria

```{r, echo=FALSE, warning=FALSE}

nigeria1 = read_excel("ECAV-nigeria.xlsx")

nigeria = nigeria1 %>% 
  filter(complete.cases(EventName, Actor1Type, Actor1Side))

 p1= nigeria %>%
   ggplot(aes(x = fct_infreq(EventName)))+
   geom_bar()+
   scale_y_continuous(trans = 'log10')+
   labs(x="Event Type", 
         y="Number of Occurrences",
         title='')+
   theme_light()+
    theme(axis.text = element_text(size =12, face='bold'))+
    theme(axis.title = element_text(size =18, face='bold'))
  
  print(p1)

```

---
#Pro- and Anti-Government Actors
##Nigeria
```{r, echo=FALSE, warning=FALSE}

 nigeria %<>% mutate(
    ActorNew = case_when(
      Actor1Type == 1 ~ 'State',
      Actor1Type == 2 ~ 'Citizens',
      Actor1Type == 3 ~ 'Party',
      Actor1Type == 4 ~ 'Militia',
      Actor1Type == 5 ~ 'NA'))

  nigeria %<>% mutate(
    SideNew = case_when(
      Actor1Side == 1 ~ 'Anti-Government',
      Actor1Side == 0 ~ 'Pro-Government'))
  
  p2 = nigeria %>%
   ggplot(aes(x = ActorNew, y = ..count..))+
   geom_bar(aes(fill = ActorNew), show.legend = FALSE)+
   facet_wrap(~SideNew)+
   scale_y_continuous(trans = 'log10')+
   labs(x="Actor Type", 
         y="Number of Events",
         title='')+
    theme_light()+
    theme(axis.text = element_text(size =14, face='bold'))+
    theme(axis.title = element_text(size =18, face='bold'))+
    theme(strip.text = element_text(face = 'bold', size = rel(2)))
  
  print(p2)
  
```



